Title of the example word file

### 2024-10-18 word/example.qmd
tidy to only required files

# load packages using pacman
pacman::p_load(
  tidyverse, lubridate, here, rmarkdown, scales, patchwork, magrittr, janitor, # general, commonly used
  styler, # auto style your code with this addin
  # ggpubr, # ggplot extension focuses on annotations and fitted models
  # ggExtra, # ggplot extension handy for things like marginal density curves on figures
  # sjstats, pwr, # anova results
  # slider, # moving averages
  # rstatix, #pipe friendly stats
  palmerpenguins # quarto functionality
)

@@

@@

```{r dataprep, include = FALSE}
# Read in data, misc initial prep/cleaning tasks
# for example, list all the files in a folder that match a specific pattern (e.g. csv files)

files <- list.files(path = "./input_file_folder/", pattern = "*.csv")

# create a short function to read in those files one by one
# modify those files after you read them in,
# and return a dataframe
read_and_append_file <- function(fle) {
  df <- read_csv(str_c("./input_file_folder/", fle))
  # do whatever individual file level modifications you need here
  # for example, extract some string from the filename
  sss <- str_extract(string = fle, pattern = "(?<=df_).*(?=_USA_Clima)")
  df %<>% mutate(sourcefilename = fle, stringofinterest = sss)
  return(df)
}

# apply that function and return an assembled dataframe
df <- files %>% map_dfr(read_and_append_file)

# apply functions to tidy up the dataframe as necessary
df %<>% clean_names()
```

>>>>

# load packages using pacman
pacman::p_load(
  tidyverse, lubridate, here, rmarkdown, scales, patchwork, magrittr, janitor, # general, commonly used
  measurements, # most unit conversions 
  styler, # auto style your code with this addin
  # ggpubr, # ggplot extension focuses on annotations and fitted models
  # ggExtra, # ggplot extension handy for things like marginal density curves on figures
  # sjstats, pwr, # anova results
  # slider, # moving averages
  # rstatix, #pipe friendly stats
  palmerpenguins # quarto functionality
)

@@

```{r constants}
# user defined constants specific to this analysis
```

@@

```{r dataprep, include = FALSE}
# Read in data, misc initial prep/cleaning tasks
# for example, list all the files in a folder that match a specific pattern (e.g. csv files)
# 
# files <- list.files(path = "./input_file_folder/", pattern = "*.csv")
# 
# # create a short function to read in those files one by one
# # modify those files after you read them in,
# # and return a dataframe
# read_and_append_file <- function(fle) {
#   df <- read_csv(str_c("./input_file_folder/", fle))
#   # do whatever individual file level modifications you need here
#   # for example, extract some string from the filename
#   sss <- str_extract(string = fle, pattern = "(?<=df_).*(?=_USA_Clima)")
#   df %<>% mutate(sourcefilename = fle, stringofinterest = sss)
#   return(df)
# }
# 
# # apply that function and return an assembled dataframe
# df <- files %>% map_dfr(read_and_append_file)
# 
# # apply functions to tidy up the dataframe as necessary
# df %<>% clean_names()
```
